Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
make labelled variants for Mult and Approx

Thus far we have explained the model of regions as sets of index
schemes, that is
$\interp{\textit{region}}_n \in \mathcal{P}(\domainVal{}^n)$.
Figure~\ref{fig:spatial-model} defines the top-level model of the
\textit{spec} syntax, which includes the multiplicity and
approximation modifiers.

>>>>

We have explained the model of regions as sets of index
schemes, that is
$\interp{\textit{region}}_n \in \mathcal{P}(\domainVal{}^n)$.
Figure~\ref{fig:spatial-model} defines the top-level model of the
\textit{spec} syntax, which includes the multiplicity and
approximation modifiers. The domain of this interepretation
is $\textsf{Mult}(\textsf{Approx}(\mathcal{P}(\domainVal{}^n)))$
where $\textsf{Mult}$ and $\textsf{Approx}$ are labelled variants
labelling our set-basd model with additional information.

\begin{definition} The \textsf{Mult}
and \textsf{Approx} are parametric labelled variant types 
with injection function given by their definition:
%
\begin{align*}
\textsf{Mult} \, a & = \textsf{mult} \, a \mid \textsf{only} \, a \\
\textsf{Approx} \, a & = \textsf{exact} \, a \mid \textsf{lower} \, a \mid
\textsf{upper} \, a \mid \textsf{both} \, a \, a
\end{align*}
\ie{}, $\mathsf{lower}$ is an injection $\mathsf{lower} : a \rightarrow \mathsf{Approx} \, a$, and so
on. 
\label{def:mult-and-approx}
\end{definition}
%
